### 2024-01-25 docs/projects/math/wolframite/index.qmd
Wolframite - rerendered

This notebook demonstrates basic usage of [Wolframite](https://github.com/scicloj/wolframite/),

It is mostly copied and adpated from [the official demo](https://github.com/scicloj/wolframite/blob/main/dev/demo.clj).

>>>>

This notebook demonstrates basic usage of [Wolframite](https://github.com/scicloj/wolframite/) in a way that would work in visual tools supporting [Kindly](https://scicloj.github.io/kindly-noted/kindly).

It is mostly copied and adpated from [the official Wolframite demo](https://github.com/scicloj/wolframite/blob/main/dev/demo.clj).
